### 2019-08-14 paper_05_milestone_issf/article.tex
Fix more references cite[ -> citep[

\noindent
Our understanding of the dynamics of turbulence strongly influenced by a stable
density stratification has been deeply changed at the beginning of the 21st
century.
%
Studies based on large-resolution numerical simulations have shown that there
is a strongly stratified regime associated with a downscale energy cascade
\cite[]{RileyDeBruynKops2003, Lindborg2006}.
%
It has been understood that the stratified turbulence is characterised by two
important non-dimensional numbers and that the regime called ``strongly
stratified turbulence'' is obtained only for very small horizontal Froude
number and large buoyancy Reynolds number \cite[]{Billant2001,
BrethouwerBillantLindborg2007},
\begin{equation}
 F_h = \frac{\epsK}{N U^2} \ll 1,\quad \R = \frac{\epsK}{\nu N^2} > 10,
\label{eq:FhR}
\end{equation}
where $\epsK$ is the kinetic energy dissipation, $N$ the
Brunt-V\"{a}iss\"{a}l\"{a} frequency, $U$ the root-mean-square horizontal
velocity and $\nu$ the kinematic viscosity.
%
\cite{RileyLindborg2008} showed that strongly stratified turbulence is a
possible interpretation for some geophysical turbulent measurements.

\noindent In a laboratory experiment, it is very difficult to fulfill the two conditions $F_h \ll 1$ and $\R > 10$ at the same time, since this requires very large
facilities.
%
Most of stratified flows studied experimentally
correspond to a regime very different than strongly stratified geophysical
flows \cite[see for example][]{PraudFinchamSommeria2005,
AugierBillantNegrettiChomaz2013, AugierBillantChomaz2015}.
%
\cite{BrethouwerLindborg2009} and \cite{Maffioli2016} investigated numerically
the mixing produced by strongly stratified turbulence and showed that at very
small horizontal Froude number ($F_h < 0.03$) and large buoyancy Reynolds
number, the mixing efficiency tends to be independent of these parameters with
a mixing coefficient $\Gamma = \epsA/\epsK$ of the order of 0.35, where $\epsA$
and $\epsK$ are the dissipation rates of available potential energy and kinetic
energy, respectively. This value is nearly twice larger that the canonical
value 0.2 used for mixing parametrization in oceanic models. Moreover, the
effect of rotation on mixing efficiency of strongly stratified
turbulence has to be investigated.

@@

\noindent We now characterize the distribution of energy among scales by second-order
structure function, defined as
\begin{eqnarray}
S_h(r) = (S_{xx} + S_{yy} + S_{xy} + S_{yx})/2,\\
\text{with} \quad S_{ij} = \langle\overline{(u_i({\bf x}+r{\bf e}_j)-u_i({\bf x}))^2}\rangle,
\end{eqnarray}
and $\overline{\cdot}$ time average when the carriage is moving. For a
developed turbulence, and for scales larger than the dissipative scale and
lower than injection scale, we expect
$S_h(r) = C (\varepsilon r)^{2/3} = C' (rU_c^3/M)^{2/3}$, with $C$ a coefficient
approximately equal to 6 \cite[see figure 15 in][]{AugierBillantChomaz2015}.
\begin{figure}[htb]
\centerline{
\includegraphics[height=7.5cm]{paper_05_milestone_issf/Figures/exp28/normalized_S2_exp28.pdf}}
\vspace{-2mm}
\caption{Normalized second-order structure $S_h$ function as a function of
$r/M$ for $F_{hc} = 0.1$ and $\mathcal{R}_c=450$.}
\label{fig:S2}
\end{figure}
Figure~\ref{fig:S2} represents normalized second-order structure function
computed from large horizontal fields for a 12 periods forcing
experiment. Interestingly, the curve exhibits a plateau corresponding to a
$r^{2/3}$ scaling law on half a decade at a value going from $0.4$ at
$\{t/T\} = 0.31$ to $0.2$ at $\{t/T\} = 0.31$. Supposing that this range
corresponds to an inertial range, we evaluate a surrogate of the mean
dissipation rate at $\epsK \sim 0.01 U_c^3/M$. This order of magnitude is
consistent with the previous estimation by direct computation of the energy
decay.

\noindent By extrapolation of the energy dissipation rate and energy injected
at the vicinity of the carriage, we define surrogates of the turbulent
horizontal Froude and buoyancy Reynolds numbers based on the measured flow as
\begin{equation}
F_{he} \simeq \frac{\epsK}{N U^2} \simeq 0.25 F_{hc},\quad 
\R_e \simeq \frac{\epsK}{\nu N^2} \simeq 2\times10^{-2} \R_c.
\label{eq:e}
\end{equation}
For this case for $F_{hc} = 0.1$ and $\mathcal{R}_c=450$, we find
$F_{he} \simeq 0.02$ and $\mathcal{R}_e \simeq 9$. These orders of magnitude
correspond to flows for which a downscale energy cascade and horizontal spectra
with a -5/3 scaling law have been observed numerically
\cite[]{BrethouwerBillantLindborg2007, AugierBillantChomaz2015}.
%
This strongly indicates that the $r^{2/3}$ scaling law for $S_h$ is indeed
related to strongly stratified turbulence.

>>>>

\noindent
Our understanding of the dynamics of turbulence strongly influenced by a stable
density stratification has been deeply changed at the beginning of the 21st
century.
%
Studies based on large-resolution numerical simulations have shown that there
is a strongly stratified regime associated with a downscale energy cascade
\citep[]{RileyDeBruynKops2003, Lindborg2006}.
%
It has been understood that the stratified turbulence is characterised by two
important non-dimensional numbers and that the regime called ``strongly
stratified turbulence'' is obtained only for very small horizontal Froude
number and large buoyancy Reynolds number \citep[]{Billant2001,
BrethouwerBillantLindborg2007},
\begin{equation}
 F_h = \frac{\epsK}{N U^2} \ll 1,\quad \R = \frac{\epsK}{\nu N^2} > 10,
\label{eq:FhR}
\end{equation}
where $\epsK$ is the kinetic energy dissipation, $N$ the
Brunt-V\"{a}iss\"{a}l\"{a} frequency, $U$ the root-mean-square horizontal
velocity and $\nu$ the kinematic viscosity.
%
\cite{RileyLindborg2008} showed that strongly stratified turbulence is a
possible interpretation for some geophysical turbulent measurements.

\noindent In a laboratory experiment, it is very difficult to fulfill the two conditions $F_h \ll 1$ and $\R > 10$ at the same time, since this requires very large
facilities.
%
Most of stratified flows studied experimentally
correspond to a regime very different than strongly stratified geophysical
flows \citep[see for example][]{PraudFinchamSommeria2005,
AugierBillantNegrettiChomaz2013, AugierBillantChomaz2015}.
%
\cite{BrethouwerLindborg2009} and \cite{Maffioli2016} investigated numerically
the mixing produced by strongly stratified turbulence and showed that at very
small horizontal Froude number ($F_h < 0.03$) and large buoyancy Reynolds
number, the mixing efficiency tends to be independent of these parameters with
a mixing coefficient $\Gamma = \epsA/\epsK$ of the order of 0.35, where $\epsA$
and $\epsK$ are the dissipation rates of available potential energy and kinetic
energy, respectively. This value is nearly twice larger that the canonical
value 0.2 used for mixing parametrization in oceanic models. Moreover, the
effect of rotation on mixing efficiency of strongly stratified
turbulence has to be investigated.

@@

\noindent We now characterize the distribution of energy among scales by second-order
structure function, defined as
\begin{eqnarray}
S_h(r) = (S_{xx} + S_{yy} + S_{xy} + S_{yx})/2,\\
\text{with} \quad S_{ij} = \langle\overline{(u_i({\bf x}+r{\bf e}_j)-u_i({\bf x}))^2}\rangle,
\end{eqnarray}
and $\overline{\cdot}$ time average when the carriage is moving. For a
developed turbulence, and for scales larger than the dissipative scale and
lower than injection scale, we expect
$S_h(r) = C (\varepsilon r)^{2/3} = C' (rU_c^3/M)^{2/3}$, with $C$ a coefficient
approximately equal to 6 \citep[see figure 15 in][]{AugierBillantChomaz2015}.
\begin{figure}[htb]
\centerline{
\includegraphics[height=7.5cm]{paper_05_milestone_issf/Figures/exp28/normalized_S2_exp28.pdf}}
\vspace{-2mm}
\caption{Normalized second-order structure $S_h$ function as a function of
$r/M$ for $F_{hc} = 0.1$ and $\mathcal{R}_c=450$.}
\label{fig:S2}
\end{figure}
Figure~\ref{fig:S2} represents normalized second-order structure function
computed from large horizontal fields for a 12 periods forcing
experiment. Interestingly, the curve exhibits a plateau corresponding to a
$r^{2/3}$ scaling law on half a decade at a value going from $0.4$ at
$\{t/T\} = 0.31$ to $0.2$ at $\{t/T\} = 0.31$. Supposing that this range
corresponds to an inertial range, we evaluate a surrogate of the mean
dissipation rate at $\epsK \sim 0.01 U_c^3/M$. This order of magnitude is
consistent with the previous estimation by direct computation of the energy
decay.

\noindent By extrapolation of the energy dissipation rate and energy injected
at the vicinity of the carriage, we define surrogates of the turbulent
horizontal Froude and buoyancy Reynolds numbers based on the measured flow as
\begin{equation}
F_{he} \simeq \frac{\epsK}{N U^2} \simeq 0.25 F_{hc},\quad 
\R_e \simeq \frac{\epsK}{\nu N^2} \simeq 2\times10^{-2} \R_c.
\label{eq:e}
\end{equation}
For this case for $F_{hc} = 0.1$ and $\mathcal{R}_c=450$, we find
$F_{he} \simeq 0.02$ and $\mathcal{R}_e \simeq 9$. These orders of magnitude
correspond to flows for which a downscale energy cascade and horizontal spectra
with a -5/3 scaling law have been observed numerically
\citep[]{BrethouwerBillantLindborg2007, AugierBillantChomaz2015}.
%
This strongly indicates that the $r^{2/3}$ scaling law for $S_h$ is indeed
related to strongly stratified turbulence.
